Cybersecurity is too important to be left to the specialists \\(Abstract 20 January, Paper 27th)

### 2019-01-16 ITiCSE2019.tex
Minor tweaks
Abstract

\begin{document}
\title{Are We Teaching Cybersecurity (and how well)?\\(Abstract 20 January, Paper 27th)}
%\title{What Do We Mean By Cybersecurity?}  Tom's original was this
%\titlenote{}
%\subtitle{Extended Abstract}
%\subtitlenote{}
\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

@@

\def\IntroYear{2014}  % when BCS started asking for CyberSecurity
\begin{abstract}
There are many facets to CyberSecurity education: we address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''. We consider particularly the UK perspective, where the British Computer Society accredits computing degrees, and (since \IntroYear) insists on a certain CyberSecurity element in all such.
\end{abstract}

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
\begin{enumerate}
\item The person in the street --- probably not. ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
\section{Policy Context}

>>>>

\begin{document}
\title{Cybersecurity is too important to be left to the specialists
\\(Abstract 20 January, Paper 27th)}
%\title{What Do We Mean By Cybersecurity?}  Tom's original was this
%\titlenote{}
%\subtitle{Extended Abstract}
%\subtitlenote{}
\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

@@

\def\IntroYear{2014}  % when BCS started asking for CyberSecurity
\begin{abstract}
There are many facets to CyberSecurity education: we address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''.  (Cyber)Security (if thought about at all) has hisorically been left to specialists, sometimes called ``Information Assurance'', which worked, even if not well, in a waterfall model.  The Agile and DevOps trends have changed devleopment, but not themselves the view of security. Over the last few years, there has been a recogition of the need for change, exemplified by ``DevSecOps''. But if security is not to be left to the experts, then the generalist must know about it.

We consider particularly the UK perspective, where the British Computer Society accredits computing degrees, and (since \IntroYear) insists on a certain CyberSecurity element in all such.
\end{abstract}

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
\begin{enumerate}
\item The person in the street --- probably not. ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
\pagebreak
\section{Policy Context}
